\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}

\geometry{a4paper, margin=1in}

\title{Your Report Title Here}
\author{Your Name Here}
\date{\today}

% Set up fancy headers and footers
\pagestyle{fancy}
\fancyhf{} % Clear existing headers and footers
\rhead{\thepage} % Right-aligned page number
\renewcommand{\headrulewidth}{0pt} % Remove header line

\begin{document}
	
	\begin{titlepage}
		
		\centering
		\vspace*{2cm}
		\textbf{\LARGE Your Report Title Here}
		\vspace{1cm}
		

		
		\vfill
		
		\textbf{Your Name Here}
		
		\vspace{1cm}
		\today
	\end{titlepage}
	
	\begin{center}
		\textbf{In the Name of Allah}
	\end{center}
	\begin{abstract}
		Your abstract text goes here.
	\end{abstract}
	
	\section{Introduction}
	Introduce your topic and the purpose of the report here.
	
	\section{Background}
	Provide any background information that your reader will need.
	
	\section{Methodology}
	Explain how you conducted your research.
	
	\section{Results}
	Present your findings here.
	
	\section{Discussion}
	Discuss the implications of your results.
	
	\section{Conclusion}
	Sum up the report and any final thoughts.
	
	\begin{thebibliography}{9}
		\bibitem{latexcompanion} 
		Michel Goossens, Frank Mittelbach, and Alexander Samarin. 
		\textit{The \LaTeX\ Companion}. 
		Addison-Wesley, Reading, Massachusetts, 1993.
		
		\bibitem{einstein} 
		Albert Einstein. 
		\textit{Zur Elektrodynamik bewegter Körper}. (German) 
		[\textit{On the Electrodynamics of Moving Bodies}]. 
		Annalen der Physik, 322(10):891–921, 1905.
		
		\bibitem{knuthwebsite} 
		Knuth: Computers and Typesetting,
		\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}
	\end{thebibliography}
	
\end{document}
